Modeling the impacts of park access on health outcomes: a choice-based accessibility approach

### 2019-03-05 manuscript.Rnw
Change author order.

\author{Nico Boyd\affilnum{1}, Gregory S. Macfarlane\affilnum{2},
John E. Taylor\affilnum{1}, and Kari Watkins\affilnum{1}}
\runninghead{Boyd, et al.}

\affiliation{\affilnum{1}School of Civil and Environmental Engineering, Georgia Institute of Technology\\
\affilnum{2}Civil and Environmental Engineering Department, Brigham Young University}

>>>>

\author{Gregory S. Macfarlane\affilnum{1}, Nico Boyd\affilnum{2},
John E. Taylor\affilnum{2}, and Kari Watkins\affilnum{2}}
\runninghead{Boyd, et al.}

\affiliation{\affilnum{1}Civil and Environmental Engineering Department, Brigham Young University\\
\affilnum{2}School of Civil and Environmental Engineering, Georgia Institute of Technology}
